Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeastern Taiwan

### 2020-01-31 analysis/paper/paper.Rmd
edit statistical analysis section

By standardizing standard deviation in each data set, the coefficients of variation values allows us to directly compare variation in samples measured with different units or means. We take this as our measurement of standardisation in vessel shape: lower CV values reflect higher standardisation, and thus increased craft specialisation in the community. <!-- note that our samples are different in size,, say something about how the CV values are robust to different sample sizes, see if there is a citation that is relevant here -->

>>>>

By standardizing standard deviation in each data set, the coefficients of variation (CV) values allows us to directly compare variation in samples measured with different units or means. CV values are robust to different sample sizes in the condition that the mean-standard deviation relationship is linear and positive since standard deviation is scaled to the mean [@Eerkens2001, pp.496]. We take this as our measurement of standardisation in vessel shape variables: lower CV values reflect higher standardisation, and thus increased craft specialisation in the community.
